### 2025-04-03 scripts/Paper-analysis.Rmd
figure names

```{r}
library(ggplot2)
library(knitr)
library(xtable)
library(dplyr)
library(tidyr)
```
### Figure 1

@@

```
### Sliding window analysis

@@

```
```{r}
# Sliding window for GC content
p.lines.GC = ggplot(d.reduced.median.plot, aes(x, GC/5000 * 100))+
  geom_hline(yintercept = 0, linetype='dashed')+
  theme_bw()+
  geom_path(aes(group=PTU, alpha=normalized_n))+
  facet_wrap(~PTU, scales="free_x", nrow=3)+
  ylab("GC content (5kb sliding window)")+
  labs(alpha="% of plasmids within PTU")+
  theme(panel.grid=element_blank())+  
  scale_x_continuous(labels = function(x) x / 1000) +
  xlab("Position on plasmid (kb)")+
  theme(legend.position = c(0.8, 0.2))
ggsave(p.lines.GC, file='../results/GC-content.pdf',
       width=10, height=6)

@@

```{r}
overall.median.GC = d.reduced %>% filter(x<50000) %>%
  group_by(x) %>%
  summarise(y=mean(GC_n),
            n=length(GC_n))
p.overall.average.GC = ggplot(overall.median.GC, aes(x, y/5000 * 100))+
  geom_line()+
  theme_bw()+
  theme(panel.grid = element_blank())+
  geom_hline(yintercept = 50, linetype='dashed')+
  ylab("GC content (per kb)")+
    scale_x_continuous(labels = function(x) x / 1000) +
  xlab("Position on plasmid (kb)")+
  theme(axis.text=element_text(colour="black"))
p.overall.average.GC
# Save
ggsave(p.overall.average.GC, file='../results/GC-mean-overall.pdf', 
       width=5, height=2)
```

>>>>

```{r}
library(ggplot2)
library(knitr)
library(xtable)
library(dplyr)
library(tidyr)
```

```
### Figure 1

@@

### Sliding window analysis

@@

```
```{r}
# Sliding window for GC content
p.lines.GC = ggplot(d.reduced.median.plot, aes(x, GC/5000 * 100))+
  geom_hline(yintercept = 0, linetype='dashed')+
  theme_bw()+
  geom_path(aes(group=PTU, alpha=normalized_n))+
  facet_wrap(~PTU, scales="free_x", nrow=3)+
  ylab("GC content (5kb sliding window)")+
  labs(alpha="% of plasmids within PTU")+
  theme(panel.grid=element_blank())+  
  scale_x_continuous(labels = function(x) x / 1000) +
  xlab("Position on plasmid (kb)")+
  theme(legend.position = c(0.8, 0.2))
ggsave(p.lines.GC, file='../results/Figure-S1-GC-content.pdf',
       width=10, height=6)

@@

```{r}
overall.median.GC = d.reduced %>% filter(x<50000) %>%
  group_by(x) %>%
  summarise(y=mean(GC_n),
            n=length(GC_n))
p.overall.average.GC = ggplot(overall.median.GC, aes(x, y/5000 * 100))+
  geom_line()+
  theme_bw()+
  theme(panel.grid = element_blank())+
  geom_hline(yintercept = 50, linetype='dashed')+
  ylab("GC content (per kb)")+
    scale_x_continuous(labels = function(x) x / 1000) +
  xlab("Position on plasmid (kb)")+
  theme(axis.text=element_text(colour="black"))
p.overall.average.GC
# Save
ggsave(p.overall.average.GC, file='../results/Figure-S1-GC-mean-overall.pdf', 
       width=5, height=2)
```
